Approximation as Differentiation: Notes

### 2025-05-25 main/category-of-families.tex
Give the construction of the internal hom in Fam(C).

\noindent In $\Fam(\cat{C})$ the objects $(X, \partial X)$ are thus sets $X$ paired with indexed families
$\partial X: X \to \cat{C}$ and morphisms $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ are functions
$f: X \to Y$ paired with morphisms $\partial f: \partial X \to \partial \reindex{Y}{f}$ in
$\Func{X}{\cat{C}}$.

>>>>

\noindent In $\Fam(\cat{C})$ the objects $(X, \partial X)$ are thus all sets $X$ paired with indexed families
$\partial X: X \to \cat{C}$ and the morphisms $(f, \partial f): (X, \partial X) \to (Y, \partial Y)$ are all
functions $f: X \to Y$ paired with morphisms $\partial f: \partial X \to \partial \reindex{Y}{f}$ in
$\Func{X}{\cat{C}}$.

\todo{Maybe unpack why these are true}

\begin{proposition}
\label{prop:Grothendieck:fam-inherits}
\item
\begin{enumerate}
\item If $\cat{C}$ is locally small then so is $\Fam(\cat{C})$.
\item If $\cat{C}$ has binary products then so does $\Fam(\cat{C})$.
\end{enumerate}
\end{proposition}

### 2025-05-25 main/higher-order.tex
Give the construction of the internal hom in Fam(C).

$\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed. Both are therefore unsuitable for
interpreting higher-order programs. However the following is a special case of a construction due to
\citet{nunes2023}:

@@

>>>>

$\Fam(\FinVect)$ nor $\Fam(\LatGal)$ provide appropriate notions of composition for automatic differentiation
and Galois slicing respectively, but neither is Cartesian closed. Neither is therefore suitable for
interpreting higher-order programs. However the following is a special case of a construction due to
\citet{nunes2023}:

@@

If $\cat{C}$ has all small products and also biproducts, then the internal hom $\internalHom{(X, \partial
X)}{(Y, \partial Y)}$ in $\Fam(\cat{C})$ is the object $(Z, \partial Z)$, where:
\begin{itemize}
\item the indexing set $Z$ is the hom-set $\Fam(\cat{C})(X,Y)$, which is indeed a set by
\propref{Grothendieck:fam-inherits};
\item the indexed family $\partial Z$ is the family of objects $\prod_{X}\reindex{\partial Y}{f}$ for every
${(f, \partial f): (X, \partial X) \to (Y, \partial Y)}$.
\end{itemize}
